Hydras \& Co.

### 2022-12-27 doc/chapter-fol.tex
documentation on FOL (draft)

@@

@@

@@

>>>>

\section{Introduction}

@@

\subsubsection{A toy language}
In order to show a few simple examples of statements and proofs, we define a small language with very few symbols:
two constant symbols: $a$ and $b$, a function symbol $f$ (of arity 1), three propositional symbols $A$, $B$ and $C$, a one-place predicate symbol $P$, and a binary relational symbol $R$.

\inputsnippets{folExample2/ToyDef}

\subsubsection{Languages for Arithmetic}

@@

\begin{remark}[Variables]
In O'Connor's formalization of first-order logic, the variables are \gallina terms of the form \texttt{var $L$ $i$}, where $L$ is
 a language and $i$ a natural number. 
Although other choices may be considered : PHOAS, de Bruijn indices, etc,  we   respect this representation, in order not to break long proof scipts which use this representation (please look at \cite{OConnor05} for a related discussion).

\end{remark}
\subsubsection{Examples}

With our toy language, we can build the following terms, respectively written $a$, $f(a)$ and $f(f(v_1))$ in usual mathematical notation.

Writing these terms in bare \gallina syntax would result in quite clumsy scripts. Thus, we may use a still experimental notation scope which allows us to write/print terms and formulas in a 
notation similar to \coq's.

We put both the associated \coq{} terms, in bare \gallina{} syntax, and with a still experimental and provisional notation, defined in
~\href{../theories/html/hydras.MoreAck.FOL_notations.html}{MoreAck.FOL\_notations}).

\inputsnippets{folExample2/toyNotation}

\inputsnippets{folExample2/smallTerms}

@@

\begin{remark}[bound variables]
\inputsnippets{folExample2/boundVars}  
\end{remark}
